\LARGE \bf Sandhi: An open source alternative to LabVIEW

### 2014-01-19 paper.tex
few more additions

Sandhi is a pure python implementation using the GNU Radio's framework. It reaps advantage of Scilab's computational engine via sciscipy. Sciscipy is an Application Programming Interface aimed at Inter Process Communication with Scilab, when in the workspace of Python programming language.

@@

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{csim.png}
	\caption{Continuous time simulation flowgraph}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{dsim.png}
	\caption{Discrete time simulation flowgraph}
	\label{overflow}
\end{figure}

>>>>

Sandhi is a pure python implementation using the GNU Radio's framework. It reaps advantage of Scilab's computational engine via Sciscipy. Sciscipy is an Application Programming Interface aimed at Inter Process Communication with Scilab, when in the workspace of Python programming language.

@@

\subsection{GNU Radio Advanced Scheduler}

GNU Radio is an open source radio implementation which is used by the Electrical Engineering community for the purpose of digital signal processing. It has a rich module of device drivers and thereby supports a range of devices. GNURadio is very promising visual programming tool as it makes it very easy for the developer to abstract his code, and provides a very easy to use framework to the developer. On top of all these advantages it is open source and hence making it potentially very attractive alternative to control system enthusiasts, who use SIMULINK/ LabVIEW for doing rapid prototyping of control schemes.

A flow graph in GNU Radio is visual representation of data flow between two or more nodes, and these nodes are called blocks (which process the flowing data). The main shortcoming of GNU Radio is its stock application scheduler's lack of ability to process closed loop in visual flow graph. This is a design choice made by the GNU Radio developers to keep the system efficient for real time applications. The job of the scheduler is to dispatch threads generated from visual flow graph; the way GNU Radio overcomes this lack of closed loops in flow graph is to implement loops in code of the block. For example, block of AGC(Automatic Gain Control) implements closed loop system in its code itself(hardcoded). This way GNU Radio ensures that flow graph always, is an acyclic directed graph.

However, this may not be very helpful for control system engineers since lot of their flow graphs have closed loops and hardcoding the blocks to make it open loop is counter-intutive. Thus, a separate scheduler called GNU Radio Advanced Scheduler is being developed to incorporate closed loop flow graphs. It uses C++ libaries such as Theron(concurrency library), PMC(Polymorphic Message Container for C++ library) etcetra.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{csim.png}
	\caption{Continuous time simulation flow graph}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{dsim.png}
	\caption{Discrete time simulation flow graph}
	\label{overflow}
\end{figure}
